\documentclass{article}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{calc,pict2e,picture}
\usepackage{textgreek,textcomp,gensymb,stix}
\title{Design Plan}
\begin{document}
  \maketitle
  \section*{Project Summary}
  The Signaler program calculates increasing prime numbers and then outputs one number every second. 
  \section*{Features Targeted}
  \subsection*{Man Page}
  Make a sample man page for the program that explains how it works and any errors it may return.
  \subsection*{LaTeX Design Plan/Write Up}
  Have the Project write up and design plan in LaTeX code.
  \subsection*{-s flag}
  Start at number after flag is set instead of after 2.
  \subsection*{-r flag}
  Program runs in reverse where numbers output are counting down instead of up. 
  \subsection*{-e flag}
  The program exits once the next prime number to be output is past the number following the -e flag.
  \subsection*{-t flag}
  The number following the -t flag tells the program how many seconds are between outputs.
  \section*{Architecture}
  \subsection*{Data}
Two struct will be used; one for the flags on the command line and one for the array of prime number and two counters for iterating through the array.\\
struct app{\\
\qquad uint64\_t start\_val\\
\qquad uint64\_t end\_val\\
\qquad uint32\_t sec\_val\\
\qquad bool reverse\\
}
struct prime\_{\\
\qquad char *primes\\
\qquad long prime\_counter\\
\qquad long index\_counter\\
}
  \subsection*{Significant Functions}
  bool calc\_prime(struct prime *p)\\
  \qquad This function will calculate prime numbers.\\
  void output\_prime(struct prime *p)\\
  \qquad This function will output prime numbers.\\
  void set\_flags(struct app *a)\\
  \qquad These functions will set the flags that are present.\\
  void signal\_handler()\\
  \qquad This function will handle any signals that are sent to the program.\\
  \section*{Plan}
  The plan for this project is to start with being able to calculate any prime numbers and add them to an array *primes. After each second, the program will output one prime number from the array. This will go on until the correct signal is received by the program to exit.
  \section*{User Interface}
Uses the CLI. The user will initiate the program with no flags/one flag/multiple flags. The program will not end until the proper signal is sent by the user to the program. 
\\
\\
\end{document}

