\documentclass{article}

\usepackage{hyperref}
\usepackage{multicol}

\title{Project Writeup}
\author{Richard Soto}
\begin{document}
  \maketitle

  \section{Project Summary}
  Write a pair of programs, a dispatcher and a listener, to act as a communication relay.
  The program dispatcher passively accepts text from standard input, exiting normally on EOF.
  The program listener will print out any text that was sent to a running instance of dispatcher. When dispatcher exits, so too does listener.

  \section{Challenges}
  Working across multiple threads that had their own threads was a new challenge for sure. I learned quite a bit about
  to manage synchronization between threads, and polling. Without the instructors assistance this would have been a much more difficult task.
  I am glad to have had the exposure as I am sure these topics will come up again.

  \section{Successes}
  Ultimately, the program was able to run as expected. With much trial and error, we were able to produce a working
  product that met most of the requirements. We also did well with team members dealing with other issues mid project
  and we were able to adjust accordingly.

  \section{Lessons Learned}
  Again, design was a big part of this project. We had to make sure that we were able to handle all of the edge cases.
  If I could start over, I would have spent more time on the design and less time on the implementation. Specifically,
  I would have tried to tie the destruction of a given thread to the destruction of the thread that spawned it. This would
  have made the code much more readable and easier to understand, while being much more manageable.
\end{document}

